---
title: "plotly Practice"
author: "Marcela Castro León"
date: "April 15, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
library(tidyr)
library(dplyr)

```

## Basic scatterplot

Basic scatterplot: use mode = "markers"

```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(mtcars, x=mtcars$wt,y=mtcars$mpg, mode="markers")
```

## Add colors

```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(mtcars, x=mtcars$wt,y=mtcars$mpg, mode="markers", color=as.factor(mtcars$cyl))
```

## add continuous colors

```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(mtcars, x=mtcars$wt,y=mtcars$mpg, mode="markers", color=mtcars$disp)
```

## change point 

Use variable hp to show the point
```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(mtcars, x=mtcars$wt,y=mtcars$mpg, mode="markers", color=as.factor(mtcars$cyl),size=mtcars$hp)
```

## 3D Scaterplot

```{r, warning=FALSE, message=FALSE, echo=TRUE}
set.seed(2016-07-21)
temp <- rnorm(100, mean=30, sd=5)
pressue <- rnorm(100)
dtime <- 1:100
plot_ly(x = temp, y=pressue, z=dtime, type="scatter3d", mode="markers", color=temp)
```

## Time series

Ploting a time series dataset airmiles (see time(airmiles)) 
```{r, warning=FALSE, message=FALSE, echo=TRUE}
data("airmiles")
plot_ly(x=time(airmiles), y=airmiles, mode="lines")
```

## Multi lIne graphs

```{r, warning=FALSE, message=FALSE, echo=TRUE}
data("EuStockMarkets")
stock <- as.data.frame(EuStockMarkets) %>% 
    gather(index, price) %>% 
    mutate(time = rep(time(EuStockMarkets),4))
plot_ly(stock, x = stock$time, y=stock$price, color=stock$index)
```

## Histogram

```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(x = precip, type="histogram")
```

## Boxplot

```{r, warning=FALSE, message=FALSE, echo=TRUE}
plot_ly(iris, y = iris$Petal.Length, color=iris$Species, type= "box")
```

## Heatmap
Are useful for displaying three dimensional data in two dimensions, 
using color for the third dimension,
```{r, warning=FALSE, message=FALSE, echo=TRUE}
terrain1 <- matrix(rnorm(100*100),nrow=100, ncol=100)
plot_ly(z=terrain1, type= "heatmap")
```


## Surface 

```{r, warning=FALSE, message=FALSE, echo=TRUE}
terrain2 <- matrix(sort(rnorm(100*100)),nrow=100, ncol=100)
plot_ly(z=terrain2, type= "surface")
```


## Choroplet map

```{r, warning=FALSE, message=FALSE, echo=TRUE}
state_pop <- data.frame(State=state.abb, Pop=as.vector(state.x77[,1]))
state_pop$hover <- with(state_pop, paste(State,'<br>',"Population:", Pop))
borders <- list(color = toRGB("red"))
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
plot_ly(state_pop, z=state_pop$Pop, text = state_pop$hover, locations = state_pop$State, type= 'choropleth', locationmode = 'USA states', color=state_pop$Pop, colors= 'Blues', marker=list(line=borders)) %>% layout(title='US Population in 1975', geo=map_options)
```


